### 2021-07-09 rad-icfp-2021/appendix1.tex
fixing proof appendix

\begin{tabular}{c l r}
    & $\nabla_A$ !prod(A)! & \\
    =&  $\nabla_A$(!reduce * 1 A!) & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> y) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> x) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !map2 (a,b -> a*b*z) A$_3$ A$_2$! & \\
    & \Big)(1)\\
     $\stackrel{\beta-reduction}{=}$  & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> y) A$_0$ A) in! & !A$_1$=shift1L A! \\
    & !let A$_2$ = map2 (x,y -> x) A$_0$ A in! & !A$_2$= A$_0$!\\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 (a,b -> a*b*1) A$_3$ A$_2$! & !map2 * A$_3$ A$_2$! \\
    = & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$=shift1L A! &\\
    & !let A$_3$ = scanr * 1 A$_1$! & \\
    & !map2 * A$_3$ A$_0$! & forward substitution !A$_2$! \\
    $\stackrel{\eta-reduction}{=}$ & !map2 * (scanr * 1 shift1L A)! &\\
    & \quad\quad\quad\quad !(shift1R (scanl * 1 A))! &
\end{tabular}
 \end{proof}

@@

    \begin{tabular}{c l r}
    & $\nabla_A$ !sum(A)! & \\
    = & $\nabla_A$ !reduce + 0 A! & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> 1) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !map2 (a,b -> a*b*z) A$_3$ A$_2$! & \\
    & \Big)(1)\\
    $\stackrel{\beta-reduction}{=}$  & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> 1) A$_0$ A) in! & !A$_1$=OnesLike(shift1L(A))! \\
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & !A$_2$=OnesLike(A)!\\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 (a,b -> a*b*1) A$_3$ A$_2$! & !map2 * A$_3$ A$_2$! \\
    = & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = OnesLike(shift1L(A))! & forward substitution \\
    & !let A$_2$ = OnesLike(A)! & forward substitution \\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 * A$_3$ A$_2$! & \\
    = & !let A$_3$ = scanr * 1 OnesLike(shift1L(A)) in! & !A$_3$=OnesLike(A)!\\
    & !map2 * A$_3$ OnesLike(A)! & forward substitution \\
    = & !map2 * OnesLike(A) OnesLike(A)! & \\
    = & !OnesLike(A)!
    \end{tabular}
\end{proof}

@@

Let's call this term !Y!.
For convenience, let us also rewrite !map2 * B (map (x -> 1) A)! 
as !let C = map (x -> 1) A in map2 * B C!.

@@

\begin{tabular}{c l r}
    & $\nabla$ !dot(A,B)! & \\
    = & $\nabla$ !let C = map (x -> 1) A in map2 * B C! & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl + 0 A) in!  \hspace{4cm}\rdelim\}{5}{3mm}[\parbox{40mm}{same reduction\\as previously}]\\
    & !let A$_1$ = shift1L (map2 (x,y -> 1) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !Y(map2 (a,b -> a*b*z) A$_3$ A$_2$)! & \\
    & \Big)(ZerosLike(A),1)\\
    = & !Y(OnesLike(A))! & \\
    = & !let C$_1$ = map2 (a,b -> b) A B in! & !C$_1$ = B! \\
    & !let C$_2$ = map2 (a,b -> a) A B in! & !C$_2$ = A! \\
    & !(map2 * C$_1$ OnesLike(A), map2 * C$_2$ OnesLike(A))!  &\\
    = & !let C$_1$=B in! & forward substitution \\
    & !let C$_2$=A in! & forward substitution \\
    & !(map2 * C$_1$ OnesLike(A),! & !C$_1$! \\
    & !map2 * C$_2$ OnesLike(A))! & !C$_2$! \\
    = & !(map2 * B OnesLike(A), map2 * A OnesLike(A))! \\
    = & !(B, A)!
\end{tabular}

>>>>

\begin{tabular}{c l r}
    & $\nabla_A$ !prod(A)! & \\
    =&  $\nabla_A$(!reduce * 1 A!) & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> y) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> x) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !map2 (a,b -> a*b*z) A$_3$ A$_2$! & \\
    & \Big)(1)\\
     $\stackrel{\beta-reduction}{=}$  & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$ = shift1L (map2 (x,y -> y) A$_0$ A) in! & !A$_1$=shift1L A! \\
    & !let A$_2$ = map2 (x,y -> x) A$_0$ A in! & !A$_2$= A$_0$!\\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 (a,b -> a*b*1) A$_3$ A$_2$! & !map2 * A$_3$ A$_2$! \\
    = & !let A$_0$ = shift1R (scanl * 1 A) in! & \\
    & !let A$_1$=shift1L A! &\\
    & !let A$_3$ = scanr * 1 A$_1$! & \\
    & !map2 * A$_3$ A$_0$! & forward substitution !A$_2$! \\
    $\stackrel{\eta-reduction}{=}$ & !map2 * (scanr * 1 shift1L A)! &\\
    & \quad\quad\quad\quad !(shift1R (scanl * 1 A))! &
\end{tabular}

 \end{proof}

@@

    \begin{tabular}{c l r}
    & $\nabla_A$ !sum(A)! & \\
    = & $\nabla_A$ !reduce + 0 A! & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = shift1L! & \\
    & \quad\quad !(map2 (x,y -> 1) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !map2 (a,b -> a*b*z) A$_3$ A$_2$! & \\
    & \Big)(1)\\
    $\stackrel{\beta-reduction}{=}$  & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = shift1L! & !A$_1$=OnesLike(shift1L(A))! \\
    & \quad\quad !(map2 (x,y -> 1) A$_0$ A) in! & \\
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & !A$_2$=OnesLike(A)!\\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 (a,b -> a*b*1) A$_3$ A$_2$! & !map2 * A$_3$ A$_2$! \\
    = & !let A$_0$ = shift1R (scanl + 0 A) in! & \\
    & !let A$_1$ = OnesLike(shift1L(A))! & forward substitution \\
    & !let A$_2$ = OnesLike(A)! & forward substitution \\
    & !let A$_3$ = scanr * 1 A$_1$ in! & \\
    & !map2 * A$_3$ A$_2$! & \\
    = & !let A$_3$ = scanr * 1! & !A$_3$=OnesLike(A)!\\
    &  \quad\quad!OnesLike(shift1L(A)) in! & \\
    & !map2 * A$_3$ OnesLike(A)! & forward substitution \\
    = & !map2 * OnesLike(A) OnesLike(A)! & \\
    = & !OnesLike(A)!
    \end{tabular}

\end{proof}

@@

Let's call this term !Y!.
For convenience, let us also rewrite \\
!map2 * B (map (x -> 1) A)! 
as !let C = map (x -> 1) A in map2 * B C!.

@@

\begin{tabular}{c l r}
    & $\nabla$ !dot(A,B)! & \\
    = & $\nabla$ !let C = map (x -> 1) A in map2 * B C! & \\
    $\defeq$ & \Big(!fun z ->! & \\ 
    & !let A$_0$ = shift1R (scanl + 0 A) in! &\\
    & !let A$_1$ = shift1L (map2 (x,y -> 1) A$_0$ A) in! & \\ 
    & !let A$_2$ = map2 (x,y -> 1) A$_0$ A in! & \\
    & !let A$_3$ = scanr * 1 A$_1$ in! &\\
    & !Y(map2 (a,b -> a*b*z) A$_3$ A$_2$)! & \\
    & \Big)!(ZerosLike(A),1)!\\
    = & !Y(OnesLike(A))! & (same reduction as previously)\\
    = & !let C$_1$ = map2 (a,b -> b) A B in! & !C$_1$ = B! \\
    & !let C$_2$ = map2 (a,b -> a) A B in! & !C$_2$ = A! \\
    & !(map2 * C$_1$ OnesLike(A),! &\\ 
    & !map2 * C$_2$ OnesLike(A))!  &\\
    = & !let C$_1$=B in! & forward substitution \\
    & !let C$_2$=A in! & forward substitution \\
    & !(map2 * C$_1$ OnesLike(A),! & !C$_1$! \\
    & !map2 * C$_2$ OnesLike(A))! & !C$_2$! \\
    = & !(map2 * B OnesLike(A),! & \\
    & !map2 * A OnesLike(A))! & \\
    = & !(B, A)!
\end{tabular}
